Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-01-28 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Changed duplicate reference
Fixed missing reference
UUpdate tex.

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores. 
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore two variations of the anomalous diffusion modelling approach. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies two sets of parameters based on the solute's radial distance from the
  closest pore center. Next, we generalize Markov state models, treating the
  configurational state of the system as a Markov process, each
  of which having separate transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative differences 
  between MD and Markov state dependent model-generated trajectories may limit 
  its usefulness. Finally, we demonstrate how one can use these models to 
  estimate flux of a solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. This work 
  helps to connect microscopic chemically-dependent solute motions that do not
  follow simple diffusive behavior with macroscopic membrane performance.

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at
  scale.~\cite{hatakeyama_nanoporous_2010}

@@

  Using a bottom-up modeling approach, we can parameterize single particle
  behavior by extracting their trajectories from MD simulations and studying
  the properties that have the greatest influence on solute dynamics. With this
  information, we can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. Fortunately, there is an abundance of information encoded in
  the complex solute trajectories. Into a model, we can incorporate fluctuations and
  time-dependent correlations in solute position as well as the length of time
  solutes are trapped. We can add further detail by integrating
  this time series analysis with our knowledge of the primary trapping
  mechanisms as well as the solute's changing chemical environment within the
  heterogeneous membrane.

@@

  We constructed our first model by applying the rigorous theoretical
  foundation already developed to describe the motion of particles exhibiting
  non-Brownian, or anomalous, transport
  behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this
  study.~\cite{klages_anomalous_2008}

@@

  We treated our system as an FBM process subordinate to a CTRW, or
  subordinated FBM (sFBM) for short. We fit sFBM models in two ways: First, we
  parameterized solute motion using a single set of parameters fit to a
  hypothesized anomalous diffusion (AD) model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's
  radial distance from the closest pore center. This allows us to include
  different dynamical behavior of solutes observed within the pore region
  versus within the monomer tails.

  Where applicable, the sFBM model provides a way to propagate information
  about solute trajectories gathered at the microsecond time scale to realistic
  experimental time scales. It can also confirm the importance of assumed
  solute-membrane interactions used to define the model's functional form, and
  suggest missing components. It can help researchers formulate hypotheses to
  explain why a certain set of parameters is characteristic to a specific
  solute.

@@

  The goal of this work is not to definitively determine which modeling
  approach is better but to evaluate their performance independently because
  they both have potential value dependent on a given research study's goals.
  The AD approach provides a systematic way to compare the dynamical behavior
  of different solutes based solely on the time series of their center of mass
  positions. The process of choosing the correct AD approach provides its own
  mechanistic insight since it requires a thorough analysis of solute time
  series behavior. One can simulate different solutes, compare the fit model
  parameters and relate them back to differences in solute size and chemical
  composition. The MSDDM characterizes explicitly defined trapping mechanisms,
  providing a clear picture of solute behavior while in each trapped state as
  well as the equilibrium occupation of each trapping state.  It is possible to
  use the two modelling approaches in tandem, the AD approach to identify
  mechanisms, and the MSDDM to characterize mechanisms.

  We evaluate the two modeling approaches by using them to characterize the
  dynamical behavior of the four fastest moving solutes studied in our previous
  work: methanol, urea, ethylene glycol and acetic acid. In addition to moving
  quickly, allowing them to extensively explore membrane structural space,
  these solutes have a range of chemical functionality and experience each of
  the three trapping mechanisms to different extents.

@@

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data. We ran MD simulations using the leapfrog integrator with 
  h-bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
  a pressure of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and
  the v-rescale thermostat respectively. We recorded frames every 0.5 ns.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha$ 
  parameter we calculated by maximizing the likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of $t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. A standard way of 
  doing this, with easily estimated parameters, is by adding an exponential 
  cut-off to the power law so the dwell time distribution is now proportional 
  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model. 
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  %BJC3: not sure how to cite fbm
  %TODO: cite github page for fbm
  We used the Python package \texttt{fbm} to generate exact simulations of FBM
  and our own Python implementation of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{S-section:flm_correlation} of the Supplemental Material for
  validation of the approach).

@@

  A Markov state model (MSM) decomposes a time series into a set of discrete
  states with transitions between states defined by a transition probability
  matrix, $T$, which describes the conditional probability of moving to a
  specific state given the previously observed
  state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
%  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
%  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
%  dimensional reduction which are often necessary to identify representative states.

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. Therefore, there is no need to
  apply any algorithmic approaches to identify and decompose our system into
  discrete states. The states we have chosen include all combinations of
  trapping mechanisms in the pore and out of the pore (see
  Table~\ref{table:states}). They assume that there are no significant kinetic
  effects resulting from solute conformational changes or pore size
  fluctuations. We use the same radial cut-off (0.75 nm) as in the AD approach to
  differentiate the pore and tail region. We define a hydrogen bond to exist
  if the distance between donor, D, and acceptor, A, atoms is less than 3.5
  \AA~and the angle formed by $D-H \cdots A$ is less than
  30$\degree$.~\cite{luzar_effect_1996} We define a sodium ion to be associated
  with an atom if they are within 2.5 \AA~of each other, as determined in our
  previous work~\cite{coscia_chemically_2019}

@@

  \begin{figure}
  \centering
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
  \caption{urea}\label{fig:URE_trajectories}
  \end{subfigure}
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
  \caption{ethylene glycol}\label{fig:GCL_trajectories}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
  \caption{methanol}\label{fig:MET_trajectories}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
  \caption{acetic acid}\label{fig:ACH_trajectories}
  \end{subfigure}
  \caption{Representative trajectories generated from each solute exhibit hops
	  between periods of entrapment, characteristic of a CTRW. Solute
	  dynamics show radial dependence, represented by the color at each
	  time point. The longest periods of entrapment typically occur when
	  solutes drift far from the pore center and into the tails.
  }\label{fig:solute_trajectories}
  \end{figure}

  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian as well as a more general L\'evy stable
	  distribution. The L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions since Gaussian hops are convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  We observe that in some cases, solute trajectories extracted from our MD
  simulations display non-stationary behavior. We defined the perceived
  equilibration time point for each solute based on the time at which the
  number of solutes inside the pores and tails stabilized
  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
  evidence of non-stationary solute behavior after the perceived equilibration
  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
  the MSD of the solutes calculated using trajectory data from the first and
  second halves of the ``equilibrated" simulation time. Ethylene glycol and
  methanol show considerable differences between the MSDs of the two halves.
  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
  shapes of their MSD curves are also very similar (see
  Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).

@@

  We obtain reasonable predictions of the MD simulated MSDs when we
  parameterize AD models with all available data after the perceived
  equilibration time. The MSD curves generated from the 1 and 2 mode models
  are overlayed with the MD simulated MSDs for comparison in
  Figure~\ref{fig:anomalous_msds}. The associated parameters for the 1 and 2
  mode models are presented in Figures~\ref{fig:1mode_parameters}
  and~\ref{fig:2mode_parameters}.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the one mode model reveal differences in dynamics
	  between solutes. (a) We parameterized Gaussian,
	  $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
	  distributions to describe solute hop lengths. We assume the mean
	  ($\mu$) to be zero for these distributions and there to be no
	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
	  hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
	  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
	  solute dwell times. Lower values of $\alpha$ lead to heavier power
	  law tails and higher values of $\lambda$ truncate the distribution at
	  lower dwell times. (c) Finally, we parameterized the hop
	  autocorrelation function, $\gamma(H)$, to describe the degree of
	  correlation between hops. Higher values of $H$ display closer to
	  Brownian behavior.}\label{fig:1mode_parameters}
  \end{figure}

@@

  To create an MSDDM for each solute, we determined the state sequence associated
  with each solute trajectory and then generated emission distributions of fluctuations
  within each state as well as transitions between states. In theory, one could 
  parameterize separate transition distributions for those which occur in the tails 
  versus in the pores, however this would lead to a broken correlation structure 
  similar to that seen in the two mode AD models.

>>>>

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores.

  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore two variations of the anomalous diffusion modeling approach. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies two sets of parameters based on the solute's radial distance from the
  closest pore center.

  Next, we generalize Markov state models, treating the
  configurational state of the system as a Markov process, each
  state of which has  
  %MRS10:
  %each having separate
  distinct transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative differences 
  between MD and Markov state dependent model-generated trajectories may limit 
  its usefulness.

  Finally, we demonstrate how one can use these models to 
  estimate flux of a solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. This work 
  helps to connect microscopic chemically-dependent solute motions that do not
  follow simple diffusive behavior with macroscopic membrane performance.

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to 
  %MRS10: synthesis implies chemical synthesis, this is really assembly - but produce is more general. 
  %synthesize 
  produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

@@

  Using a bottom-up modeling approach, we can parameterize single particle
  behavior by extracting 
  %MRS10: their is referring to behavior, which is singular - changing grammar.
  %their 
  particle
  trajectories from MD simulations and studying
  the properties that have the greatest influence on solute dynamics. With this
  information, we can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. Fortunately, there is an abundance of information encoded in
  the complex solute trajectories. 
  %MRS: moving clause out from top.
  %Into a model, 
  We can incorporate fluctuations and
  time-dependent correlations in solute position 
  %MRS added:
  into transport models, 
  as well as the length of time
  solutes are trapped. We can add further detail by integrating
  this time series analysis with our knowledge of the primary trapping
  mechanisms as well as the solute's changing chemical environment within the
  heterogeneous membrane.

@@

  We constructed our first model by applying the 
  %MRS10: tweaked
  existing
  rigorous theoretical
  foundation 
  %already developed 
  to describe the motion of 
  particles 
  %MRS10: added specificity
  simulated at the atomistic level
  %exhibiting
  which exhibit
  non-Brownian, or anomalous, transport
  behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this
  study.~\cite{klages_anomalous_2008}

@@

  We treated our system as an FBM process subordinate to a CTRW, or
  subordinated FBM (sFBM) for short. We fit sFBM models in two ways: First, we
  parameterized solute motion using a single set of parameters fit to a
  hypothesized anomalous diffusion (AD) model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's
  radial distance from the closest pore center. This allows us to include
  different dynamical behavior of solutes 
  %MRS10: added, to show that this is informed by looking at the trajectories.
  previously
  observed within the pore region
  versus within the monomer tails.

  %MRS10: tweaked, also made plural since multiple models are built.
  %Where applicable, the sFBM model 
  Where sufficiently close to observed data, these fitted sFBM models
  provides a way to propagate information
  about solute trajectories gathered at the microsecond time scale to realistic
  experimental time scales. They can also confirm the importance of assumed
  solute-membrane interactions used to define the model's functional form, and
  suggest missing components. They can help researchers formulate hypotheses to
  explain why a certain set of parameters is characteristic to a specific
  solute.

@@

  The goal of this work is not to definitively determine which modeling
  approach is better but to evaluate their performance independently because
  they both have potential value dependent on a given research study's goals.
  The AD approach provides a systematic way to compare the dynamical behavior
  of different solutes based solely on the time series of their center of mass
  positions. The process of choosing the correct AD approach provides its own
  mechanistic insight since it requires a thorough analysis of solute time
  series behavior. One can simulate different solutes, compare the fit model
  parameters and relate them back to differences in solute size and chemical
  composition. The MSDDM characterizes explicitly defined trapping mechanisms,
  providing a clear picture of solute behavior while in each trapped state as
  well as the equilibrium occupation of each trapping state.  It is possible to
  use the two modeling approaches in tandem, the AD approach to identify
  mechanisms, and the MSDDM to characterize mechanisms.

  We evaluate the two modeling approaches by using them to characterize the
  dynamical behavior of the four fastest moving solutes studied in our previous
  work: methanol, urea, ethylene glycol and acetic acid. In addition to moving
  %MRS10: tweaked, may not be quick in absolute terms.
  more 
  quickly
  than other solutes studied previously, 
  allowing them to extensively explore membrane structural space,
  these solutes have a range of chemical functionality and experience each of
  the three trapping mechanisms to different extents.

@@

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data. We ran MD simulations using the leapfrog integrator with 
  hydrogen bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
  a pressure of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and
  the v-rescale thermostat respectively. We recorded frames every 0.5 ns.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha$ 
  parameter we calculated by maximizing the 
  %MRS10: added for precision
  log
  likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of $t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. A standard way of 
  doing this, with easily estimated parameters, is by adding an exponential 
  cut-off to the power law so the dwell time distribution is now proportional 
  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model. 
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the 
  %MRS10:
  log 
  likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  %BJC3: not sure how to cite fbm
  %TODO: cite github page for fbm
  We used the Python package \texttt{fbm} to generate exact simulations of FBM
  %MRS10: add a reference to where your implementation can be found.
  and our own Python implementation of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{S-section:flm_correlation} of the Supplemental Material for
  validation of the approach).

@@

  A Markov state model (MSM) decomposes a time series into a set of discrete
  states with transitions between states defined by a transition probability
  matrix, $T$.  
  %MRS10: split sentence for readability.
  $T$ describes the conditional probability of moving to a
  specific state given the previously observed
  state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
%  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
%  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
%  dimensional reduction which are often necessary to identify representative states.

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. Therefore, there is no need to
  apply any algorithmic approaches to identify and decompose our system into
  discrete states. The states we have chosen include all combinations of
  trapping mechanisms in the pore and out of the pore (see
  Table~\ref{table:states}). They assume that there are no significant kinetic
  effects resulting from solute conformational changes or pore size
  fluctuations. We use the same radial cut-off (0.75 nm) as in the AD approach to
  differentiate the pore and tail region. We define a hydrogen bond to exist
  if the distance between donor, D, and acceptor, A, atoms is less than 3.5
  \AA~and the angle formed by $D-H \cdots A$ is less than
  30$\degree$.~\cite{luzar_effect_1996} We define a sodium ion to be associated
  with an atom if they are within 2.5 \AA~of each other, as determined in our
  previous work.~\cite{coscia_chemically_2019}

@@

  \begin{figure}
  \centering
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
  \caption{urea}\label{fig:URE_trajectories}
  \end{subfigure}
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
  \caption{ethylene glycol}\label{fig:GCL_trajectories}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
  \caption{methanol}\label{fig:MET_trajectories}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
  \caption{acetic acid}\label{fig:ACH_trajectories}
  \end{subfigure}
  \caption{
    %MRS10: added
    Three
    representative trajectories generated from each solute exhibit hops
	  between periods of entrapment, characteristic of a CTRW. Solute
	  dynamics show radial dependence, represented by the color at each
	  time point. The longest periods of entrapment typically occur when
	  solutes drift far from the pore center and into the tails.
  }\label{fig:solute_trajectories}
  \end{figure}

  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian 
          ``as well as'' is ambiguous, can mean ``in addition to'' or ``similar in quality to''
          %as well as 
          almost as well as
          a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  We observe that in some cases, solute trajectories extracted from our MD
  simulations display non-stationary behavior. We defined the perceived
  equilibration time point for each solute based on the time at which the
  number of solutes inside the pores and tails stabilized
  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
  evidence of non-stationary solute behavior after the perceived equilibration
  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
  the MSD of the solutes calculated using trajectory data from the first and
  second halves of the ``equilibrated" simulation time. Ethylene glycol and
  methanol show considerable differences between the MSDs of the two halves.
  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
  shapes of 
  %MRS10: which of the solutes does ``their'' refer to?  Be more explicit.
  their MSD curves are also very similar (see
  Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).

@@

  We obtain reasonable predictions of the MD simulated MSDs when we
  parameterize AD models with all available data after the perceived
  equilibration time. The MSD curves generated from 
  %MRS10: added
  both 
  %MRS10: more grammatically correct to say ``one and two'' instead of ``1 and 2''
  the one and two mode models
  are overlayed with the MD simulated MSDs for comparison in
  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
  mode models are presented in Figures~\ref{fig:1mode_parameters}
  and~\ref{fig:2mode_parameters}.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the one mode model reveal differences in dynamics
	  between solutes. (a) We parameterized Gaussian,
	  $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
	  distributions to describe solute hop lengths. We assume the mean
	  ($\mu$) to be zero for these distributions and no
	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
	  hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
	  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
	  solute dwell times. Lower values of $\alpha$ lead to heavier power
	  law tails and higher values of $\lambda$ truncate the distribution at
	  lower dwell times. (c) Finally, we parameterized the hop
	  autocorrelation function, $\gamma(H)$, to describe the degree of
	  correlation between hops. 
          %MRS10: tweaked
          Simulations with higher values of $H$ display behavior closer to
	  the Brownian limit.}\label{fig:1mode_parameters}
  \end{figure}

@@

  To create an MSDDM for each solute, we determined the state sequence associated
  with each solute trajectory 
  %MRS10: added for clarity to make sure people who how the state sequence was determined.
  based on the geometric indicators of the states indicated in Table~\ref{table:states}.
  and then generated emission distributions of fluctuations
  within each state as well as transitions between states. In theory, one could 
  parameterize separate transition distributions for those which occur in the tails 
  versus in the pores, however this would lead to a broken correlation structure 
  similar to that seen in the two mode AD models.
